---
title: "p8105_hw5_ks3663"
author: "Kee-Young Shin"
date: "November 3, 2018"
output: github_document
---

```{r}
library(tidyverse)
library(purrr)
library(RCurl)

```

## Problem 1
```{r}

files_list = paste0("./data/", list.files("./data"))
files_list

output = map_df(files_list, read.csv) %>% 
  add_column(files_list, .before = "week_1") %>% 
  mutate(files_list = str_replace(files_list, "./data/", ""),
         files_list = str_replace(files_list, ".csv", "")) %>% 
  separate(files_list, into = c("Control Arm", "Subject ID"), sep = "_") %>% 
  janitor::clean_names()
output

```

```{r}
# make spaghetti plot comparing both arms 
output %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  arrange(control_arm, subject_id) %>% 
  group_by(subject_id) %>% 
  ggplot(aes(x = week, y = observation, color = subject_id, group = subject_id)) + 
    geom_line() + 
    facet_wrap(~control_arm) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

When looking at the control group, there seems to be no apparent trend over time, fluctuating up and down. The experiment group, however, shows a clear pattern: the observation increases over time. For the control group, there are many moments wherein the observation dips below 0. Conversely, the observation is negative for only a couple of subjects on week 1, after which there are no negative observations recorded.


## Problem 2
```{r}
# read in data and clean names 
homicide_df = read.csv(text = getURL("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) %>% 
  unite(city_state, city:state, sep = ", ") %>% 
  janitor::clean_names()

homicide_df %>% 
  group_by(victim_race) %>% 
  summarize(count = n())
homicide_df %>% 
  mutate(victim_age = as.numeric(victim_age)) %>% 
  summarize(avg = mean(victim_age))
homicide_df %>% 
  group_by(victim_sex) %>% 
  summarize(count = n())
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(count = n()) %>% 
  arrange(-count)
```

The raw dataset contains `r nrow(homicide_df)` homicides committed in 50 large U.S. cities. The race of the victims that were most commonly murdered were black with 33361 homicides, while the least targeted race were Asians with 685. The average age of the victims in this dataset were 33.3, indicating that many were middle aged. The majority of the victims were male with a total count of 40739 males compared to 7209 females. Chicago, IL had the most homicides in this dataset with a count of 5535. Lastly, there is a recorded observation of 1 homicide for Tulsa AL. This outlier is most likely an error made during the creation of this dataset, since it seems Tulsa is not a real city in AL. 

```{r}
# create new data frame containing total homicide and unsolved homicide 
homicide_df_summarized = homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_homicide = n(),
      unsolved_homicide = sum(disposition == "Closed without arrest") 
      + sum(disposition == "Open/No arrest"))
```

```{r}
# run prop.test for Baltimore, MD
baltimore_results = prop.test(x = homicide_df_summarized %>% filter(city_state == "Baltimore, MD") %>% pull(unsolved_homicide), n = homicide_df_summarized %>% filter(city_state == "Baltimore, MD") %>%  pull(total_homicide)) %>% 
  broom::tidy()

# pull estimated proportion and confidence interval
baltimore_results %>% 
  select(estimate, conf.low, conf.high) 

```

```{r}
# run prop.test on all city-states
prop_test_output = homicide_df_summarized %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(output = map2(.x = homicide_df_summarized %>% pull(unsolved_homicide), 
              .y = homicide_df_summarized %>% pull(total_homicide), 
              ~prop.test(x = .x, n = .y)),
         output = map(output, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  select(c("city_state", "estimate", "conf.low", "conf.high"))
  
```

```{r}
# create plot showing estimate for all city-states and their Confidence Intervals
prop_test_output %>% 
  mutate(city_state = as.factor(city_state),
         city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
    geom_point() +
    geom_errorbar(ymin = prop_test_output$conf.low, 
                  ymax = prop_test_output$conf.high) +
    theme(axis.text.x = element_text(angle = 80, hjust = 1))

```

Chicago, IL had the highest proportion of unsolved homicide, while Richmond, VA had the lowest. The cities with narrower confidence intervals indicate that their respective homicide counts are relatively larger than those with larger confidence intervals. Tulsa, AL, which was an outlier and an error in the dataset, had a very large confidence interval since its homicide count was only 1. 
